### 2017-01-08 MSSM/MSSM.tex
Adding more figs + some words on systematic uncertainties

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}
\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 6.2\% for
data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
applied to all processes for which the normalisation was estimated 
using \ac{MC} samples.
\subsubsection*{Identification, isolation and trigger efficiencies}
\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
\subsubsection*{Jet energy scale uncertainty}
\subsubsection*{B-tag scale factors}
\subsubsection*{\MET resolution and response}
\subsubsection*{Background normalisation}
\subsubsection*{Theory uncertainties}

@@

\subsection{Model--independent results}
\label{sec:mssm_results_modelindep}

\subsection{Interpretation in MSSM benchmark scenarios}
\label{sec:mssm_results_modeldep}

@@

>>>>

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}
\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 6.2\% for
data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
applied to all processes for which the normalisation is estimated 
using \ac{MC} samples.
\subsubsection*{Identification, isolation and trigger efficiencies}
The uncertainty on electron and muon identification, isolation, and
trigger efficiency amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
isolation uncertainty amounts to 6\% in the \etau and \mutau channels
and 12\% in the \tautau channel, with an additional 7\% uncertainty
on the tau trigger efficiency added in quadrature for that channel \cite{CMS-PAS-HIG-16-037}. This
uncertainty is split between a part that is correlated between the channels, 
a 5\% (10\%) uncertainty in the \etau and \mutau (\tautau) channels. The uncorrelated 
part amounts to 3\% (9.2\%) for the \etau and \mutau (\tautau) channels.
The uncertainties on lepton/hadronic tau identificiation, isolation and 
trigger efficiency are applied to all processes for which the normalisation
is estimated using \ac{MC} samples.
\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
The uncertainty on the jet$\rightarrow\Pgt_{h}$ fake rate
is 20\% \cite{cms-tau-2015}. This uncertainty is applied
to those backgrounds where the normalisation is estimated from \ac{MC} and
where the hadronic taus are mimicked by jets, that is the \Zellell background
with a jet faking a hadronic tau, the \Wjets background in the fully hadronic
channel, and the \ttbar background with a jet faking a hadronic tau. 
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
The $\Pe\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 10-30\%,
depending on the anti-electron discriminator used \cite{cms-tau-2015}. This uncertainty is 
applied to the \Zellell background with the hadronic tau faked by an electron.
The $\Pgm\rightarrow\Pgt_{h}$ fake rate uncertainty ranges from 20-30\%, depending
on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
background with the hadronic tau faked by a muon.
\subsubsection*{Jet energy scale uncertainty}
The uncertainties on the jet-energy corrections are applied
by shifting the jet energy up and down by the \pT~ and $\eta$ dependendent
uncertainty, and evaluating the the change in process normalisation in
each category. Where the change in normalisation is non-negligible the
uncertainty is applied. It ranges from 1--10\% depending on process and category.
\subsubsection*{B-tag scale factors}
Uncertainties on the b-tagging efficiency and light jet mis-tagging
rates are given as a function of jet \pT~ and $\eta$ for the 
medium working point of the \ac{CSV}v2 discriminator \cite{cms-btag-run2}.
The b-tagging scale factors are are varied within these uncertainties
and the overall change in normalisation for each process in each category is
evaluated. If the change in normalisation is non-negligible this
uncertainty is applied. The uncertainty varies from 1--5\%.
\subsubsection*{\MET resolution and response}
\subsubsection*{Background normalisation}
\subsubsection*{Theory uncertainties}

@@

\subsection{Model--independent results}
\label{sec:mssm_results_modelindep}
The \mTtot~ distributions in the no b-tag and b-tag
categories of all channels, after the fit to the observed
data has been performed, are shown in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em}.
The signal of the 3 neutral Higgs bosons at \mA=1 TeV and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid 
on the total transverse mass distributions. The signal peaks twice due to the presence of a light Higgs boson
with mass compatible with 125 GeV in this model, which is necessary to incorporate the Higgs boson
observed at 125 GeV into the model.

\begin{figure}[h!]
\begin{center}
\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
\end{center}
\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
of the \mutau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid. Note that, to incorporate
the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_mt}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
\end{center}
\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
of the \etau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_et}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
\end{center}
\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_tt}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[no b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
\subfloat[b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
\end{center}
\caption{Distributions of \mTtot~ in the (a) no b-tag and (b) b-tag categories 
of the \tautau channel. The signal of the 3 neutral Higgs bosons at \mA=1 TeV 
and \tanb=50 in the $m_{h}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_em}
\end{figure}

None of these distributions show hints of a significant excess. The
95\% upper limits on $\sigma\times$BR are shown in figure \ref{fig:mssm_results_limits}a
for gluon--gluon fusion and in figure \ref{fig:mssm_results_limits}b for b--associated
production. All channels and categories are combined. 
\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-a.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_009-b.pdf}}
\end{center}
\caption{Upper limits at 95\% CL for (a) the gluon--gluon fusion production
process and (b) the b--associated production process. All four final states and 
all categories are combined for these limits \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_limits}
\end{figure}

A comparison of the expected limits
per channel is shown in figure \ref{fig:mssm_results_limits_breakdown}a for gg$\phi$ production
and in figure \ref{fig:mssm_results_limits_breakdown}b for bb$\phi$ production.
These figures show that the \mutau channel is the most sensitive at masses up to 
200 GeV, beyond which the \tautau channel becomes more sensitive. The \etau
channel is always slightly less sensitivie than the \mutau channel. The \emu channel
is the least sensitive over a large part of the parameter space, until it overtakes the 
\etau channel in sensitivity at 1.6 TeV and is slightly more sensitive than the
\mutau channel at 3.2 TeV. The \emu channel becomes more sensitive at higher masses as
a narrower binning of the \mTtot~ distribution is possible than for the other channels.
The \mTtot~ distribution for the high mass signals is therefore wide enough not to
fall entirely into the last bin used for the fit. This means at high mass this channel
benefits more from the shape discrimination between signal and backgrounds than
the other channels.

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_010-a.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_010-b.pdf}}
\end{center}
\caption{Expected upper limits at 95\% CL for (a) gluon--gluon fusion and (b) b--associated production,
comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
and \emu (gold) channels \cite{CMS-PAS-HIG-16-037}. For masses below 200 GeV the \mutau channel is the most sensitive,
while the \tautau channel dominates for higher masses. The \etau channel is always
slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive, 
until at around 1.6 TeV it starts to overtake the \etau channel, with the sensitivity at 3.2 TeV 
being similar or slightly better than the \mutau channel. FIXME REMAKE PLOT?}
\label{fig:mssm_results_limits_breakdown}
\end{figure}

\subsection{2D likelihood scans}
\label{sec:mssm_results_2D}

\subsection{Interpretation in MSSM benchmark scenarios}
\label{sec:mssm_results_modeldep}
The results are interpreted in two MSSM benchmark scenarios: the $m_{\text{h}}^{\text{mod+}}$
scenario and the hMSSM scenario. Both scenarios are described in chapter THEORY.

Figure \ref{fig:mssm_mhmodp_2016} shows the expected (dashed line and grey bands) and
observed (blue shaded area bounded by solid line) exclusion of the search presented in this chapter
in the \mA-\tanb~ plane of the $m_{\text{h}}^{\text{mod+}}$ scenario. The red shaded band
indicates the area that is excluded due to the lack of a light Higgs boson with a mass compatible
with 125 GeV. Compared with the most sensitive limits set during Run 1 of the \ac{LHC} these
limits at high \tanb~ have improved by around 300 GeV.

@@

Figure \ref{fig:mssm_hmssm_2016} shows the expected (dashed line and grey bands)
and observed (blue shaded area bounded by solid line) exclusion of the search
presented in this chapter in the \mA-\tanb~ plane of the hMSSM scenario. 
MENTION FEATURE
